---
title: "Chicken Wheights Analysis "
output: "html_document"
author: "Tahani AlHarbi"
date: "04/10/2020"
---



#### **Description:**

An experiment was conducted to measure and compare the effectiveness of various feed 
 supplements on the growth rate of chickens.
```{r}

```



```{r chickwts, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
library(tidyverse)
```






#####  To get better known of our dataset:

#### **Data head**: 

```{r}
knitr::kable(head(chickwts))

```
#### **Data tail**

```{r}

knitr::kable (tail(chickwts))

```
#### **Summary Data:**


```{r}
knitr::kable((summary(chickwts)))

```



####  **Descriptive statistics:** 



show the distribution of weight compare to type of feed.

```{r}
boxplot(weight~feed,data=chickwts, main="Chicken Weights",
        ylab="Weight", xlab="Feed") 
```





#### **To get the mean and the SD of the dataset:**

```{r}
chickwts %>% 
  group_by(feed) %>% 
  summarise(n = n(),
            avg = mean(weight), 
            sd1 = sd(weight)) %>%
  knitr::kable()

```

####  **Including Plots:**

```{r}
ggplot (chickwts, aes(feed, weight)) +
  geom_jitter(width = 0.3) +
  stat_summary(fun.data = mean_sdl, 
               fun.args = list(mult = 1), 
               col = "red")
```



#### **inferential statistics:** 
##### **Anova**

```{r}
knitr::kable(anova (fm1 <- lm(weight ~ feed, data = chickwts)))

```





#### **Histogram of residuals:**
```{r}
residuals <- resid(lm(weight ~ feed, chickwts))
hist(residuals)
```

